\sysfull

### 2018-04-13 paper/hwswsetup.tex
methodology section revised (almost complete)

We evaluated \sys in two power supply environments: (i)  \emph{intermittent} and (ii) \emph{fixed} (to benchmark the intermittent power supply results). In the experiments with intermittent power supply, we evaluated \sys using a WISP\,5.1~\cite{wisp5,wisp}---energy-harvesting platform build around a MSP430FR5969~\cite{wolverine} MCU with 64\,kB of FRAM. We powered the WISP using RF signal generator~\cite{} \todo{Add reference to signal generator}{Przemek} emitting 20\,dBm sinusoidal wave at 915\,MHz.  Signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic antenna~\cite{atlas2015}. For distance-controlled experiments, we affixed WISP at two paper protrusions around 10\,cm from the surface of the table (parallel to, and at the edge of, table surface). Antenna of the signal generator was facing WISP directly and located at three distances, $d=\{15, 30, 50\}$\,cm, from WISP. For task coalescing experiments, an additional distance of $d=60$\,cm was considered. Both antennas were parallel to each other and no physical objects were located between the WISP and signal generator antenna. For continuous power experiments we used an alternative setup with MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad}, which had the same MCU as WISP. In all the experiments the timing measurements were performed using either the Saleae~\cite{saleae} logic analyzer (for intermittent power experiments) or TI Code Composer Studio (for fixed power experiments). Both type of experiments are explained in the following section.

>>>>

We evaluated \sys in two power supply environments: (i)  \emph{intermittent} and (ii) \emph{fixed} (to benchmark the intermittent power supply results). In the experiments with intermittent power supply, we evaluated \sys using a WISP\,5.1~\cite{wisp5,wisp}---energy-harvesting platform build around a MSP430FR5969~\cite{wolverine} MCU with with 64\,kB of non-volatile (FRAM) memory and and 2\,kB of volatile memory (SRAM). MCU was running on X\,MHz clock cycle \todo{Check clock frequency}{Przemek} We powered the WISP using RF signal generator~\cite{} \todo{Add reference to signal generator}{Przemek} emitting 20\,dBm sinusoidal wave at 915\,MHz.  Signal generator was connected to the Liard RFMAX S9028PCRJ 8\,dBic antenna~\cite{atlas2015}. For distance-controlled experiments, we affixed WISP at two paper protrusions around 10\,cm from the surface of the table (parallel to, and at the edge of, table surface). Antenna of the signal generator was facing WISP directly and located at three distances, $d=\{15, 30, 50\}$\,cm, from WISP. For task coalescing experiments, an additional distance of $d=60$\,cm was considered. Both antennas were parallel to each other and no physical objects were located between the WISP and signal generator antenna. For continuous power experiments we used an alternative setup with MSP-EXP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad}, which had the same MCU as WISP. In all the experiments the timing measurements were performed using either the Saleae~\cite{saleae} logic analyzer (for intermittent power experiments) or TI Code Composer Studio (for fixed power experiments). Both type of experiments are explained in the following section.
